%%----------------------------------------------------------------------
\pagetitle{Mission: Sweep and Clear}
\label{mission:sweepandclear}

\subsection{Play Area Configuration}

Place~2 Consoles, each 12'' from the play area long edges and 6'' from
the center toward the deployment zones.  No model or marker may be
deployed in base contact with a Console.

\subsection{Mission Rules}

The Connect Mission Objective short skill is available in this
scenario (see page~\pageref{sec:hack-objective}).  Engineers
receive~+3MOD and~+1B on the WIP check to connect a Console.

\subsection{End Game}

There are no special end game conditions for this mission.

\subsection{Scoring}

% The following rules determine the outcome of this mission---

\missionrule{Sectors.}  After each game round measure four
Sectors on the play area dividing the space between the deployment
zones into equal quarters and determine domination of each.

\missionrule{Search Teams.} Forward Observers not in a Null state
provide an additional~4 victory points toward Domination in this
mission.  Troopers with the Sensor special skill and not in a Null
state provide an additional~8 victory points toward Domination in this
mission. These bonuses apply cumulatively for troopers that possess
both skills.

\missionrule{Tapped Sensor Grid.}  After each game round, for each
Console they have both currently connected and a model in base
contact, players may designate a Sector in which they are considered
to have an additional~20 army points for purposes of Domination.  Both
players make this declaration simultaneously.  A Sector may be
designated twice by a player if they control both Consoles.  Note that
a Specialist is required to connect a Console per the Connect Mission
Objective skill, but any model may be in base contact to enable this
ability.

\noindent%
\begin{tabular}{L{5.85in}C{0.5in}C{0.25in}C{0.25in}}
    \rowcolor{CornflowerBlue} & \textcolor{White}{\textbf{Obj.}} & \multicolumn{2}{c}{\textcolor{White}{\textbf{Player}}}\\
  \rowcolor{CornflowerBlue}\textcolor{White}{\textbf{Condition}} &
                                                                   \textcolor{White}{\textbf{Pts}} & \textcolor{White}{\textbf{1}} & \textcolor{White}{\textbf{2}} \\
  %%
  %% ----------------------------------------------
  Dominate more Sectors following game round~1. & 1 & $\Box$ & $\Box$ \\
  \rowcolor{CornflowerBlue!10} Dominate more Sectors following game round~2. & 2 & $\Box$ & $\Box$ \\
  Dominate more Sectors following game round~3. & 3 & $\Box$ & $\Box$ \\
  \\[-9pt]
  \rowcolor{CornflowerBlue!10} Have more Consoles connected at game end. & 1 & $\Box$ & $\Box$ \\
  %%
  %% ----------------------------------------------
  \\
\multicolumn{2}{r}{\textbf{Sum:}} & $\rule{0.25in}{0.15mm}$ & $\rule{0.25in}{0.15mm}$\\
\end{tabular}
