%%----------------------------------------------------------------------
\pagetitle{Mission: Exfiltrate}
\label{mission:exfiltrate}

\subsection{Play Area Configuration}

As part of their army deployment, before placing their HVT, each
player deploys~4 Civilian models inside the half of the Exclusion Zone
(see below) on their opponent's side of the play area.  Civilians must
be placed at least~4'' away from all other Civilians.  They cannot be
placed on any terrain requiring a Climb entire order to reach.  No
model or marker may be deployed in base contact with any Civilian or
vice versa.

Once deployed, take~2 Agent and~2 Citizen importance markers (or
suitable proxies indistinguishable on the back side).  Turn them face
down, shuffle them, and randomly assign one to each of your Civilians
without being revealed to you or your opponent.

\missionrule{Exclusion Zone.}  There is an Exclusion Zone
extending~6'' on both sides of the short centerline of the play area
(12'' long total) and covering the full extent between long edges.

\subsection{Mission Rules}

The Interrogate Civilian common skill on the following page is
available in this mission.

Once a Civilian has been revealed as an Agent, it may be directly
targeted by the opposing player as an enemy troop and no penalty is
incurred by them for damaging it.

% The Synchronize Civilian common skill cannot be applied to the
% Civilians in this mission.  Instead the following Common Skill is
% available.

\subsection{End Game}

There are no special end game conditions for this mission.
%(\emph{Retreat!} applies).

\subsection{Scoring}

\missionrule{Exfiltrated.}  An Agent has been Exfiltrated if it is
wholly inside its player's deployment zone.

\missionrule{Secured.}  An Agent is Secured if it is wholly outside
the Exclusion Zone on its player's side of the play area.  An
Exfiltrated Agent is necessarily Secured, but not vice versa.

{\setlength\fboxrule{2pt}
\cfbox{CornflowerBlue}{\begin{minipage}{6.5in}
  \colorbox{CornflowerBlue}{\parbox{\linewidth-2\fboxsep}{\textcolor{White}{\textbf{\large Interrogate Civilian} \hfill Short Movement Skill}}}\\
  \colorbox{SkyBlue}{\parbox{\linewidth-2\fboxsep}{\textcolor{White}{Attack}}}

  \medskip
  \textsc{Requirements}
  \begin{squishitemize}
  \item The user must be a model (not a marker) in base contact with a
    Civilian deployed by their player.

  \item The user cannot already be in CivEvac state with a Civilian,
    unless it possesses the Doctor, Paramedic, or Chain of Command
    special skills, in which case it cannot already be in CivEvac
    state with~2 Civilians.

  \item The user cannot be Impetuous or Extremely Impetuous, including
    through the Frenzy characteristic having triggered.

  \item The user cannot possess the G: Servant or G: Synchronized
    special skills, or its Type of Troop be REM.
    
  \item The user cannot be part of a fireteam of any kind, and this
    short skill cannot be performed as part of a coordinated order.
    
%  \item The targeted Civilian cannot be in the CivEvac state with an
%    enemy model.
  \end{squishitemize}

  \medskip
  \colorbox{Gray!24}{\begin{minipage}{\linewidth-2\fboxsep}

  \medskip      
      \textsc{Effects}
      \begin{squishitemize}
      \item The user makes a Normal WIP roll to synchronize a
        designated Civilian in base contact that was placed by their
        player.  Doctors and Paramedics receive a +3 MOD on this roll.
        Models from the Tohaa or Combined Army factions (including any
        sectorial) suffer a -3 MOD.

      \item If the roll is successful, the Civilian's importance
        marker is revealed to both players if it has not already.  If,
        and only if, the Civilian is an Agent, it enters the CivEvac
        state with the user (\emph{Human Sphere}, page~95).

      \item If the roll fails, the opposing player moves the Civilian
        as far as possible following general movement rules up to 2''
        from the user.
      \end{squishitemize}
    \end{minipage}}
\end{minipage}}}

\vspace*{-5pt}

\noindent%
\begin{tabular}{L{5.85in}C{0.5in}C{0.25in}C{0.25in}}
    \rowcolor{CornflowerBlue} & \textcolor{White}{\textbf{Obj.}} & \multicolumn{2}{c}{\textcolor{White}{\textbf{Player}}}\\
  \rowcolor{CornflowerBlue}\textcolor{White}{\textbf{Condition}} &
                                                                   \textcolor{White}{\textbf{Pts}} & \textcolor{White}{\textbf{1}} & \textcolor{White}{\textbf{2}} \\
  %%
  %% ----------------------------------------------
  Have at least one of your Agents in CivEvac state at game end. & 1 & $\Box$ & $\Box$ \\
  \rowcolor{CornflowerBlue!10} Have both of your Agents in CivEvac state at game end. & 1 & $\Box$ & $\Box$ \\
  \\[-9pt]
  Have at least one of your Agents Secured at game end. & 1 & $\Box$ & $\Box$ \\
  \rowcolor{CornflowerBlue!10} Have both of your Agents Secured at game end. & 1 & $\Box$ & $\Box$ \\
  \\[-9pt]  
  Have at least one of your Agents Exfiltrated at game end. & 1 & $\Box$ & $\Box$ \\
  \rowcolor{CornflowerBlue!10} Have both of your Agents Exfiltrated at game end. & 1 & $\Box$ & $\Box$ \\
  \\[-9pt]
  Have more Agents in CivEvac state at game end than your opponent. & 1 & $\Box$ & $\Box$ \\
  %%
  %% ----------------------------------------------
  \\[-9pt]  
  \rowcolor{CornflowerBlue!10} Classified objective achieved. & 2 & $\Box$ & $\Box$ \\
  \\
\multicolumn{2}{r}{\textbf{Sum:}} & $\rule{0.25in}{0.15mm}$ & $\rule{0.25in}{0.15mm}$\\
\end{tabular}